Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-17 ms.tex
fixed spelling typo
still re-writing discussion of fits with variable f1

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, the broad 
\PLANCK~bandpasses do not allow us to adopt the same appraoch as FDS99 in 
dealing with line emission. Instead, we must subtract estimates of the 
molecular line contamination from each \PLANCK~band in order to best isolate 
the thermal continuum we wish to characterize. The most prominent molecular 
line emission in the \PLANCK~bands of interest arises from the three lowest CO 
rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
fixed. By default, we employ the best-fit \PLANCK+DIRBE global parameters of 
Table \ref{tab:global}, model 2, although our data release 
($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
Still,  the dust spectrum normalization and dust temperatures are allowed to 
vary for each line-of-sight. In order to predict the dust SED for a given 
pixel, we are thus left with two remaining degrees of freedom, and must choose 
an appropriate set of two parameters to sample and thereby constrain via MCMC. 
To determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the `IRAS convention' intensity in the 545 GHz bandpass, as 
defined in Equation \ref{eqn:inten}. With the four aforementioned global 
parameters fixed, the dust spectrum shape is determined entirely by the two 
dust temperatures, which are coupled. To constrain the dust temperatures, we 
sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we compute
the corresponding value of $T_1$, thereby determining the temperature and 
emissivity power law index for both MBB components and thus fully specifying 
the SED shape. In principle, we could sample in either $T_1$ or $T_2$, but have
chosen to sample in $T_2$ because emission from this component dominates in the
relatively high frequency bands which most strongly constrain the dust 
temperatures.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} The $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially.}
\end{center}
\end{figure}

As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
angular resolution afforded by the \PLANCK~HFI maps provides us with the 
opportunity to allow additional parameters of the two-component model, 
previously fixed by FDS99, to vary spatially. Specifically, we consider
allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
spatially constant. In such fits, there will therefore be three free 
parameters.

@@

In order for such fits to remain sufficiently constrained with an additional 
free parameter, we consider \PLANCK~maps smoothed to $1^{\circ}$ FWHM to 
boost per-pixel S/N, and pixelize at $N_{side}=64$. We also include DIRBE 
140$\mu$m and 240$\mu$m at degree resolution in the fits with free-$f_1$ fits.

% also we're adding in 100 GHz and 143 GHz, which is something not
% done in full-resolution fits

@@

\begin{equation}
\label{eqn:f1post}
P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
\end{equation}

This posterior still employs the likelihood function of Equation 
\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
\ref{equ:t2prior} remains unchanged. The prior on $f_1$ is:

>>>>

\subsection{Molecular Emission}
Because the FIRAS spectra consist of many narrow frequency bins, FDS99 were
able to discard the relatively small number of frequency intervals contaminated
by strong molecular line emission. Unfortunately, while the \PLANCK~data 
considered in this study are of high angular resolution, the broad 
\PLANCK~bandpasses do not allow us to adopt the same approach as FDS99 in 
dealing with line emission. Instead, we must subtract estimates of the 
molecular line contamination from each \PLANCK~band in order to best isolate 
the thermal continuum we wish to characterize. The most prominent molecular 
line emission in the \PLANCK~bands of interest arises from the three lowest CO 
rotational transitions: J=1$\rightarrow$0 at 115 GHz, J=2$\rightarrow$1 at 230 
GHz and J=3$\rightarrow$2 at 345 GHz, respectively affecting the \PLANCK~100, 
217 and 353 GHz bands. The J=1$\rightarrow$0 line also imparts a signal upon 
\PLANCK~143 GHz, but at a negligible level, $\sim$1000$\times$ fainter relative
to the dust continuum than J=1$\rightarrow$0 at 100 GHz.

@@

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
spatially constant. By default, we employ the best-fit \PLANCK+DIRBE global 
parameters of Table \ref{tab:global}, model 2, although our data release 
($\S$\ref{sec:release}) includes fits with the FDS99 global parameters as well.
For each line of sight, only the dust spectrum normalization and dust 
temperatures are allowed to vary. In order to predict the dust SED for a given 
pixel, we are thus left with two remaining degrees of freedom, and must choose 
an appropriate set of two parameters to sample and thereby constrain via MCMC. 
To determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the `IRAS convention' intensity in the \PLANCK~545 GHz 
bandpass, as defined in Equation \ref{eqn:inten}. With the four aforementioned 
global parameters fixed, the dust spectrum shape is determined entirely by the 
two dust temperatures, which are coupled. To constrain the dust temperatures, 
we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby determining the temperature 
and emissivity power law index for both MBB components and thus fully 
specifying the SED shape. In principle, we could sample in either $T_1$ or 
$T_2$, but have chosen to sample in $T_2$ because emission from this component 
dominates in the relatively high frequency bands which most strongly constrain 
the dust temperatures.

@@

\begin{figure}
\begin{center}
\epsfig{file=f1_1deg.eps, width=3.3in}
\caption{\label{fig:f1} $1^{\circ}$ FWHM map of $f_1$ derived from our 
low-resolution fit in which $f_1$ is allowed to vary spatially.}
\end{center}
\end{figure}

As mentioned in $\S$\ref{sec:modeling}, the combination of high S/N and high 
angular resolution afforded by the \PLANCK~HFI maps provides us with the 
opportunity to allow additional parameters of the two-component model, 
previously fixed by FDS99, to vary spatially. Specifically, we consider
allowing $f_1$ to vary, while maintaining $\beta_1$, $\beta_2$, and $q_1/q_2$
spatially constant. In principle, we could alternatively introduce a third free
 parameter by allowing $q_1/q_2$, $\beta_1$ or $\beta_2$ to vary while holding 
$f_1$ fixed. However, a model in which $f_1$ varies continuously from one line 
of sight to another is the most natural three-parameter scenario, in that $f_1$
variation can be attributed to continuous variation of the dust species' mass
fractions, whereas continuous variations in the other global parameters, which 
represent grain emission/absoprtion properties, seem less plausible.

@@

In order for our variable $f_1$ fits to remain sufficiently constrained with 
the addition of another free parameter, we consider \PLANCK~maps smoothed to 
$1^{\circ}$ FWHM for increased S/N, and pixelize at $N_{side}=64$. To best
constrain the model parameters in each pixel, we also include \PLANCK~100 GHz 
and 143 GHz, and DIRBE 140$\mu$m and 240$\mu$m, all at $1^{\circ}$ resolution.

@@

\begin{equation}
\label{eqn:f1post}
P(\tilde{I}_{545}, T_2, f_1|\vec{I}~) \propto \mathcal{L}(\vec{I}~|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
\end{equation}

This posterior still employs the likelihood function of Equation 
\ref{equ:like}, the only difference being that $f_1$ can vary from proposal to 
proposal within each individual pixel when predicting \{$\tilde{I}_{\nu_i}$\} 
with Equation \ref{eqn:inten}. The prior $P(T_2)$ from Equation 
\ref{equ:t2prior} remains unchanged. We adopt the following prior on $f_1$:
